Size-differentiated Export Flux in Different Dynamical Regimes in the Ocean

### 2021-01-27 size_differentiated_export.tex
Adresses editor's comments
Lengthen the discussion section

	A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \cite{Levy_2012, Mahadevan_2016}. Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \cite{Thomas_2013b,Klein_2009,McWilliams_2016}. In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \cite{FoxKemper_2008,Mahadevan_2016}. On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front. The distribution of relative vorticity associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity \cite{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \cite{Mahadevan_2006}. Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \cite{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through localized downwelling \cite{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}, \add{a process that might not be captured if submesoscales O(1 km) are not fully resolved} \cite{Resplandy_2019}. The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales. If the fraction of  biomass associated with such slow sinking velocities is significant, submesoscale dynamics can potentially impact the export of POC.

@@

	The advective timestep for particles is set to 1.5 hours. The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}. Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity). Particles are tracked for four weeks (28 days). Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles. Particles located deeper than the maximum winter mixed layer \cite<i.e., 100 m;>[]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.

@@

	Introducing remineralization processes significantly decreases the biomass flux. Counter-intuitively, however, the implementation of a remineralization scheme further strengthens the contribution of slower-sinking particles to the biomass flux\add{, once particles have left the euphotic layer} (Figure \ref{fig: biomass_export_remin}). This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as these particles decelerate as they remineralize. In the summer, all particle classes are similarly affected by remineralization, as downward fluxes are gravitationally-driven. In the winter, however, slower-sinking particles are exported through advective processes. Their export timescale is barely affected by remineralization processes as it only depends on local ocean dynamics. \add{Changing the remineralization timescale would therefore only affect the results in a gravitationally-driven flux: increasing the timescales (i.e. slower remineralization) would give more weight to the smaller classes, while decreasing the timescales (i.e. faster remineralization) would favor faster sinking particles to drive the downward flux. In an advectively-driven flux, however, all particles classes are equally affected by remineralization (i.e. lose 12\% of their biomass per day). While this affects the total amount of biomass flux, it does not impact the respective contributions of the different particle classes to the downward biomass flux.}

These results are robust to the range of sinking rates explored. If one considers a particle class with a sinking rate far exceeding the vertical advective velocity \cite<e.g., 100 m/day;>[]{Turner_2015}, then the associated biomass flux can be estimated by relying on the traditional 1-D paradigm, assuming $w_{tot}\approx w_s$. Combining this approximation with Equation \ref{eq: biomassjungeslope} shows that the slope of the biomass flux spectrum is positive for $\xi<5$, in which case very fast-sinking particles would dominate  vertical biomass fluxes. However, for $\xi>5$, the slope of the biomass flux spectrum becomes negative as well, meaning that the biomass flux is always dominated by the slow-sinking particle classes, regardless of the ocean dynamical regime. \change{While considered large, values of $\xi > 5$ remain realistic and fall within the range obtained from satellite-based estimates}{While values of $\xi > 5$ have been estimated by} \citeA{Kostadinov_2009} \add{using satellite data, in-situ estimated values of $\xi$ tend to range between 2 and 4.5}\cite{White_2015, Cram_2018}.

	The results of this study suggest that slow- and non-sinking particles must be considered when studying the downward flux of particulate matter in the upper ocean. The patchiness associated with both particle production and submesoscale features poses a real observational challenge to properly resolve vertical fluxes. Based on our findings, subsequent studies should focus on testing the impact of patchiness on vertical fluxes. In the wintertime, when size spectral slope is steep and submesoscale dynamics most active, vertical fluxes could be grossly underestimated depending on the level of co-occurrence between particle production and stronger vertical currents.

@@

		\item Submesoscale dynamics generally enhance the downward particulate flux by increasing the contribution of slower-sinking particles to the total flux through advective transport.   The  slower-sinking particles are found to be significant for export, and can be even make the dominant contribution under certain conditions.
		\item The contribution of slower-sinking particles to the downward biomass flux depends on the slope of the particle size spectra (i.e., the Junge Slope), that controls the relative number of particles per size class. Two cases emerge from this study:
		\begin{enumerate}
			\item If the Junge slope is smaller than 3, larger particles contribute most to vertical biomass fluxes independently of flow dynamics, as there are no mechanisms capable of selectively advecting slower-sinking particles. The system is described as gravitationally-driven.
			\item If the Junge slope is greater than 3, as most commonly observed, ocean dynamics become key for determining which particle classes dominate the downward flux. As submesoscale dynamics become more active, ageostrophic circulations leading to larger vertical velocities develop. In these conditions, downward biomass fluxes are largely driven by the slower-sinking particle classes.
		\end{enumerate}
		\item Remineralization processes \add{below the euphotic depth} logically reduce the amount of biomass flux. However, it unexpectedly enhances the role of slower-sinking particles, which are are advectively transported. The impact of remineralization \add{below the euphotic depth} is greater on faster-sinking particles since it affects both the biomass content and their sinking velocity.
	\end{enumerate}

>>>>

	A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \cite{Levy_2012, Mahadevan_2016}. Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \cite{Thomas_2013b,Klein_2009,McWilliams_2016}. In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \cite{FoxKemper_2008,Mahadevan_2016}. On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front. The distribution of relative vorticity associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity \cite{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \cite{Mahadevan_2006}. Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \cite{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through localized downwelling \cite{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}, a process that might not be captured if submesoscales O(1 km) are not fully resolved \cite{Resplandy_2019}. The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales. If the fraction of  biomass associated with such slow sinking velocities is significant, submesoscale dynamics can potentially impact the export of POC.

@@

	The advective timestep for particles is set to 1.5 hours. The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}. Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity). Particles are tracked for four weeks (28 days). Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles. %Particles located deeper than the maximum winter mixed layer \cite<i.e., 100 m;>[]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.

@@

	Introducing remineralization processes significantly decreases the biomass flux. Counter-intuitively, however, the implementation of a remineralization scheme further strengthens the contribution of slower-sinking particles to the biomass flux, once particles have left the euphotic layer (Figure \ref{fig: biomass_export_remin}). This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as these particles decelerate as they remineralize. In the summer, all particle classes are similarly affected by remineralization, as downward fluxes are gravitationally-driven. In the winter, however, slower-sinking particles are exported through advective processes. Their export timescale is barely affected by remineralization processes as it only depends on local ocean dynamics. Changing the remineralization timescale would therefore only affect the results in a gravitationally-driven flux: increasing the timescales (i.e. slower remineralization) would give more weight to the smaller classes, while decreasing the timescales (i.e. faster remineralization) would favor faster sinking particles to drive the downward flux. In an advectively-driven flux, however, all particles classes are equally affected by remineralization (i.e. lose 12\% of their biomass per day). While this affects the total amount of biomass flux, it does not impact the respective contributions of the different particle classes to the downward biomass flux.

These results are robust to the range of sinking rates explored. If one considers a particle class with a sinking rate far exceeding the vertical advective velocity \cite<e.g., 100 m/day;>[]{Turner_2015}, then the associated biomass flux can be estimated by relying on the traditional 1-D paradigm, assuming $w_{tot}\approx w_s$. Combining this approximation with Equation \ref{eq: biomassjungeslope} shows that the slope of the biomass flux spectrum is positive for $\xi<5$, in which case very fast-sinking particles would dominate  vertical biomass fluxes. However, for $\xi>5$, the slope of the biomass flux spectrum becomes negative as well, meaning that the biomass flux is always dominated by the slow-sinking particle classes, regardless of the ocean dynamical regime. While values of $\xi > 5$ have been estimated by \citeA{Kostadinov_2009} using satellite data, in-situ estimated values of $\xi$ tend to range between 2 and 4.5 \cite{White_2015, Cram_2018}.

\add{Our findings add to a rapidly growing body of literature supporting the key role of an export pathway from the upper ocean to the interior driven by vertical ocean dynamic, and directly affecting particulate carbon. This pathway is often referred to as the  ''particle-injection pump" }\cite{Boyd_2019}\add{, or "subduction hot spots" }\cite{Levy_2013, Omand_2015, Resplandy_2019}, \add{ and is consistently identified as an important mechanism to POC export} \cite{Siegel_2016, Stukel_2017, Stukel_2018, Llort_2018}. \add{Vertical mixing at submesocales, in fact, was found to be equally important for the subduction of tracers from the mixed layer to the interior, and the obduction of tracers having a subsurface maximum (e.g., nutrients)} \cite{Taylor_2020, Mahadevan_2016}.
\add{The importance of the seasonality in submesoscales dynamics highlighted in our process-oriented study supports recent findings obtained from high-resolution observations: both }\citeA{Erickson_2018} and \citeA{Bol_2018}\add{ studied glider data to conclude that the winter intensification of submesoscale dynamics can generate a large downward export of POC. The third key component to our results, additionally to the roles of submesocale dynamics and seasonality, is the contribution of smaller, slower-sinking POC to the export flux. The results presented in this work directly align with studies providing evidence that smaller particles contribute significantly to the POC flux} \cite{Baker_2017, Riley_2012, Bol_2018, Taylor_2020}.\add{ The magnitude of the downward flux driven by slow-sinking particles, however, is still uncertain and was sometimes estimated to be largely compensated by an upward flux} \cite{Resplandy_2019}, \add{indicating a possible dependence on data resolution. In our study, we piece together three key components to POC vertical fluxes to characterize limit cases where ocean conditions favor either a gravitationally- or advectively-driven POC flux. We reached the conclusion}
\remove{The results of this study suggest} that slow- and non-sinking particles \add{, compared to the magnitude of vertical currents,} should be considered when studying the downward flux of particulate matter in the upper ocean. \add{Furthermore,} the patchiness associated with both particle production and submesoscale features poses a real observational challenge to properly resolve vertical fluxes. Based on our findings, subsequent studies could focus on testing the impact of patchiness on vertical fluxes. In the wintertime, when size spectral slope is steep and submesoscale dynamics most active, vertical fluxes could be grossly underestimated depending on the level of co-occurrence between particle production and stronger vertical currents.

@@

		\item Submesoscale dynamics generally enhance the downward particulate flux by increasing the contribution of slower-sinking particles to the total flux through advective transport. The  slower-sinking particles are found to be significant for export, and can be even make the dominant contribution under certain conditions.
		\item The contribution of slower-sinking particles to the downward biomass flux depends on the slope of the particle size spectra (i.e., the Junge Slope), that controls the relative number of particles per size class. Two cases emerge from this study:
		\begin{enumerate}
			\item If the Junge slope is smaller than 3, larger particles contribute most to vertical biomass fluxes independently of flow dynamics, as there are no mechanisms capable of selectively advecting slower-sinking particles. The system is described as gravitationally-driven.
			\item If the Junge slope is greater than 3, as most commonly observed, ocean dynamics become key for determining which particle classes dominate the downward flux. As submesoscale dynamics become more active, ageostrophic circulations leading to larger vertical velocities develop. In these conditions, downward biomass fluxes are largely driven by the slower-sinking particle classes.
		\end{enumerate}
		\item Remineralization processes below the euphotic depth logically reduce the amount of biomass flux. However, it unexpectedly enhances the role of slower-sinking particles, which are are advectively transported. The impact of remineralization below the euphotic depth is greater on faster-sinking particles since it affects both the biomass content and their sinking velocity.
	\end{enumerate}
